Author's third reply to the referee report of \\ \textsc{ ``PERSISTENT HOMOLOGY FOR FUNCTIONALS'' }

### 2023-05-16 ref_reply2.tex
Sent to referee version 3

\documentclass{article}
\usepackage{csquotes}
\usepackage{hyperref}
\usepackage[margin=1in]{geometry}

@@

	\section{Second point.}
	The referee is correct in that the proposition cited from Hatcher does not actually apply in the setting as stated; in fact our lemma is not true as it was stated.
	We have consequently added the assumption that $\colim \check{H}_0(F_{\leq \bullet}) \to \check{H}_0(M)$ needs to be an isomorphism for the Mountain Pass Theorem and have changed the lemma on the essential dimension accordingly.
	We also include an example in a remark after the Mountain Pass Theorem showing that if this assumption is removed it may happen that $\check{p}_0 > 1$.
	Moreover, we added a reference in the proof of the Unstable Minimal Surface Theorem for the fact that this new assumption is satisfied for the Douglas functional, which is due to Morse's "regularity at infinity" condition.

@@

	\section{Other changes}
	We fixed a typo in the proof of the Mountain Pass Theorem: It needs to be "... , so that in particular $\cc_{1}^{\epsilon}(t) > 0$" instead of "... , so that in particular $\cc_{0}^{\epsilon}(t) > 0$".

>>>>

\documentclass{article}
\usepackage{csquotes}
\usepackage{hyperref,amsmath}
\usepackage[margin=1in]{geometry}

@@

	\section{Second point.}
	The referee is correct in that the proposition cited from Hatcher does not actually apply in the setting as stated; in fact our lemma is not true as it was stated.
	We have consequently added the assumption that $\operatorname{colim} \check{H}_0(F_{\leq \bullet}) \to \check{H}_0(M)$ needs to be an isomorphism for the Mountain Pass Theorem and have changed the lemma on the essential dimension accordingly.
	We also include an example in a remark after the Mountain Pass Theorem showing that if this assumption is removed it may happen that $\check{p}_0 > 1$.
	Moreover, we added a reference in the proof of the Unstable Minimal Surface Theorem for the fact that this new assumption is satisfied for the Douglas functional, which is due to Morse's "regularity at infinity" condition.

@@

	\section{Other changes}
	We fixed a typo in the proof of the Mountain Pass Theorem: It needs to be "... , so that in particular $\check c_{1}^{\epsilon}(t) > 0$" instead of "... , so that in particular $\check c_{0}^{\epsilon}(t) > 0$".

### 2023-05-16 ref_reply3.tex
Sent to referee version 3

\title{Author's third reply to the referee report of \\ \textsc{
		``PERSISTENT HOMOLOGY FOR FUNCTIONALS''
	}
}
\author{Bauer \and Medina-Mardones \and Schmahl}
\begin{document}
	\maketitle
	We want to thank the referee for his careful reading of our revised article, again providing very helpful commentary and uncovering many of our inaccuracies.

	\section{First point.}
	TBW
	\section{Second point.}
	TBW
	\section{third point.}
	TBW
	\section{List of typos, minor remarks and suggestions.}
	\begin{enumerate}
		\item TBW
		\item Changed as suggested (A.S.).
		\item Changed as suggested (A.S.).
		\item TBW
		\item TBW
		\item Changed as suggested (A.S.).
		\item TBW
		\item TBW
		\item TBW
		\item TBW
		\item TBW
		\item TBW
		\item TBW
	\end{enumerate}

	\section{Other changes}
	TBW
\end{document}

>>>>

\title{Author's third reply to the referee report of \\ \textsc{
		``PERSISTENT HOMOLOGY FOR FUNCTIONALS''
	}
}
\author{Bauer \and Medina-Mardones \and Schmahl}
\begin{document}
	\maketitle
	We want to thank the referee for once again reading our revised article very carefully and for taking the time to give us very helpful and detailed commentary throughout the review process going far beyond the usual scope of referee's reports. To express our gratitude, we have included a corresponding sentence in the acknowledgements section of the article.

	\section{First point}
	It was simply an oversight on our part to not include this condition. We have added it to the definition and also briefly expanded on why the restriction $G$ of $F$ in the proof of Lemma 5.13 is weakly upper-reducible if $F$ is.
	\section{Second point}
	The Eda--Kawamura result can indeed not be applied directly to the space $M$ since $M$ need not be compact. We have adapted the proof by applying the Eda--Kawamura result to each sublevel set of $F$ before passing to the colimits, which is still sufficient to reach our desired conclusion.
	\section{Third point}
	We have extended the proof of Lemma 5.11 (now Theorem 5.11) to fill the gaps left in Morse's work and make his line of reasoning using a ``related homotopy'' explicit. We promoted the statement to the status of a theorem, since the proof is quite extensive, and the statement itself is of general interest for Morse theory. 
	\section{List of typos, minor remarks and suggestions.}
	\begin{enumerate}
		\item Mentioning boundedness from below was indeed superfluous on page 26 because it follows from compactness of sublevel sets, we have removed the mention of the boundedness property.
		\item Changed as suggested.
		\item Changed as suggested.
		\item It should have indeed said ``disjoint'' instead of ``distinct''. We have also corrected this in the statement of Theorems 5.3 and 5.8.
		\item As suggested, we have distinguished the two cases where either $t_{1} \neq t_{2}$ or $t_{1} = t_{2}$.
		\item Changed as suggested.
		\item Weak upper-reducibility was indeed not needed here, we have removed the assumption.
		\item Changed as suggested.
		\item The mentioned part of the proof was indeed not quite accurate. We have implemented the suggested fix, where $q_{n}$ can be chosen such that $F(\varphi(q_{n},1)) \to t$ because of the assumption $t \geq F(\varphi(q,1)) > t - \epsilon$ that is supposed to lead to a contradiction.
		\item We changed the bounds of the interval accordingly.
		\item Changed as suggested.
		\item The entire argument has been rewritten, so some of the relevant quantities have changed. In particular, the cover by balls of radius $\delta/3$ has been changed to balls of radius $\delta/6$.
		\item Changed as suggested.
	\end{enumerate}

	\section{Other changes}
	\begin{enumerate}
		\item We have slightly changed the definition of displacement function in Definition 5.1. Before, we were paraphrasing the version by Struwe, but now we are more closely following the version by Morse--Tompkins, which requires a certain monotonicity. This actually makes the continuity assumption for displacement functions unnecessary. We have thus also removed the continuity assumption and have correspondingly removed the explanation for why we add this assumption from Remark 5.4. We have also correspondingly modified the end of the second paragraph of the proof of Lemma 5.11, where continuity of the displacement function has previously been used.
		\item We have changed the part of the proof of Lemma 5.11 where homotopies are extended from balls to the whole sublevel set insofar that we now describe the extension process before choosing a cover by finitely many balls. This removes the additional index $i$ in the description of the extension process, which improves readability.
	\end{enumerate}
\end{document}

### 2023-05-16 sec/acknowledgment.tex
After including counterexample into section 4
after second ref
Sent to referee version 3

\section*{Acknowledgements}

U.B. has been supported by the German Research Foundation (DFG) through the Collaborative Research Center SFB/TRR 109 \emph{Discretization in Geometry and Dynamics}.

A.M-M. acknowledges financial support from Innosuisse grant \mbox{32875.1 IP-ICT-1} and the hospitality of the Laboratory for Topology and Neuroscience at EPFL.

M.S. has been supported by the German Research Foundation (DFG) through	the Cluster of Excellence EXC-2181/1 \emph{STRUCTURES}, and the Research Training Group RTG 2229 \emph{Asymptotic Invariants and Limits of Groups and Spaces}.

>>>>

%!TEX root = ../func_top.tex

\section*{Acknowledgements}
The authors wish to thank an anonymous referee for his extensive feedback and valuable suggestions, which have greatly improved the present work.

U.B. has been supported by the German Research Foundation (DFG) through the Collaborative Research Center SFB/TRR 109 \emph{Discretization in Geometry and Dynamics} -- 195170736.
A.M-M. acknowledges financial support from Innosuisse grant \mbox{32875.1 IP-ICT-1} and the hospitality of the Laboratory for Topology and Neuroscience at EPFL.
M.S. has been supported by the German Research Foundation (DFG) through the Collaborative Research Center SFB/TRR 191 \emph{Symplectic Structures in Geometry, Algebra and Dynamics} -- 281071066, the Cluster of Excellence EXC 2181 \emph{STRUCTURES} -- 390900948, and the Research Training Group RTG 2229 \emph{Asymptotic Invariants and Limits of Groups and Spaces} -- 281869850.
